Analysis

### 2017-03-27 Analysis.Rmd
Add standard deviation
sd for blight evaluations is now in final data frames and initial data
visualisations

Remove "TODO" file

Fix plot titles that were incorrectly labeled "Leaf" when they should
read "Tiller"

@@

# plot joint distibution of error
rdf <- data.frame(TShB_lmm_2015$VCV)
plot_joint_random_error_dist(d = rdf,
                             title = ("2015 Leaf ShB Random Error Distribution"))
```

@@

# diagnostic line plots for treatments
plot_diagnostic_lines(d = trts,
                      x = x,
                      title = "2106 Diagnostic Plots for Leaf ShB Treatments")

@@

# plot joint distibution of error
rdf <- data.frame(TShB_lmm_2016$VCV)
plot_joint_random_error_dist(d = rdf,
                             title = ("2016 Leaf ShB Random Error Distribution"))
```

>>>>

# diagnostic line plots for replicate
plot_diagnostic_lines(d = reps,
                      x = x,
                      title = "2015 Diagnostic Plots for Tiller ShB Reps")

# posterior distributions for replicate
plot_replicate_posteriors(d = reps,
                          title = "2015 Replicate Posteriors for Tiller ShB Reps")

# diagnostic line plots for treatments
plot_diagnostic_lines(d = trts,
                      x = x,
                      title = "2015 Diagnostic Plots for Tiller ShB Treatments")

# Posterior distributions for treatment
plot_treatment_posteriors(d = trts,
                          title = "2015 Treatment Posteriors for Tiller ShB Treatments")

@@

# plot joint distibution of error
rdf <- data.frame(TShB_lmm_2015$VCV)
plot_joint_random_error_dist(d = rdf,
                             title = ("2015 Tiller ShB Random Error Distribution"))
```

@@

# diagnostic line plots for replicate
plot_diagnostic_lines(d = reps,
                      x = x,
                      title = "2016 Diagnostic Plots for Tiller ShB Reps")

# posterior distributions for replicate
plot_replicate_posteriors(d = reps,
                          title = "2016 Replicate Posteriors for Tiller ShB Reps")

# diagnostic line plots for treatments
plot_diagnostic_lines(d = trts,
                      x = x,
                      title = "2106 Diagnostic Plots for Tiller ShB Treatments")

# Posterior distributions for treatment
plot_treatment_posteriors(d = trts,
                          title = "2016 Treatment Posteriors for Tiller ShB Treatments")

@@

# plot joint distibution of error
rdf <- data.frame(TShB_lmm_2016$VCV)
plot_joint_random_error_dist(d = rdf,
                             title = ("2016 Tiller ShB Random Error Distribution"))
```
